National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2020-11-28 Manuscript_Bayesian.Rmd
added saturated models for the bayesian estimate. Not distinguishable from the REML models.

We provide the analyses of these additional analyses in the supplement.  The supplement describing these analysis is located at: https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing.

@@

## Code
All code for this analysis and a full report of the missing data imputation can be found at [https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing](https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing).

>>>>

We provide the analyses of these additional analyses in the supplement.  The supplement describing these analysis is located at: [https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing](https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing). The html document is located at: [https://osf.io/cu2gr/](https://osf.io/cu2gr/)

@@

## Code
All code for this analysis and a full report of the missing data imputation can be found at [https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing](https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing). An html document decribing the same analysis is located at: [https://osf.io/cu2gr/](https://osf.io/cu2gr/).

### 2020-11-28 Supplement_And_Analysis.Rmd
added saturated models for the bayesian estimate. Not distinguishable from the REML models.

>>>>

### Test of the Bayesian saturacted model

```{r setmodelformulaSAT}
forumula_bayesPWI_SATUR <- bf(PWI ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1+ yearsC|Id))
forumula_bayesLIFESAT_SATUR <- bf(LIFESAT ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1+ yearsC|Id))
```
```{r pwi_bayesmodelSAT}
# PWI
mod.1_bSAT <-brm(forumula_bayesPWI_SATUR, data= d_3, file ="mod.1_bS.rds", cores = 8) # note these are very large files
summary(mod.1_bSAT)
```

```{r Bayesian_pwi_predictedSAT, cache=TRUE, dependson= mod.1_b}
graph_predictions(mod.1_bSAT, "Predicted Values of Personal Well-Being")
```
```{r Bayesian_lifesat_predictedSAT, cache=TRUE, dependson= mod.2_b}
graph_predictions(mod.2_b, "Predicted Values of Life Satisfaction")
```

```{r lsbayesmodelSAT}
# LIFE SAT
mod.2_bSAT <-brm (forumula_bayesLIFESAT_SATUR, data= d_3,cores = 8, file ="mod.2_bS.rds")
summary(mod.2_bSAT)

###
tab_model(mod.1_bSAT,mod.2_bSAT)
# note these are very large files
```
